CTFEF

### 2023-09-10 Papers/FEDCIS-2023-presentation/sections/motivation.tex
added dockerfile for working with latex
some more presentation stuff
more presentation stuff
final corrections

\begin{frame}
	\frametitle{Metaprogramming}

	\begin{itemize}
		\item Metaprogramming - writing programs that analyse or modify themselves\begin{itemize}
			      \item Dynamic - metaprogramming done at run time
			      \item Static - metaprogramming done at compile time
		      \end{itemize}
		\item Makes code more expressive and resilient to change
		\item Boosts productivity
		\item Can improve performance
		\item Mostly present in garbage-collected languages at runtime\begin{itemize}
			      \item C\#
			      \item Java
			      \item Scripting languages such as Javscript or python
		      \end{itemize}
	\end{itemize}

@@

@@

	\begin{itemize}
		\item General purpose, compiled research programming language with manual memory management
		\item Built around powerful static metaprogramming features
		\item Arbitrary code can be executed at compile time\begin{itemize}
			\item Inspect the code base and report diagnostics
			\item Modify the program before it is translated to machine code
			\item Access the file system and external tools
		\end{itemize}
	\end{itemize}

>>>>

\begin{frame}
	\frametitle{Motivation}

	\begin{itemize}
		\item Metaprogramming - writing programs that analyse or modify themselves\begin{itemize}
			      \item Dynamic - metaprogramming done at run time
			      \item Static - metaprogramming done at compile time
		      \end{itemize}
		\item Makes code more expressive and resilient to change
		\item Boosts productivity
		\item Can improve performance
		\item Mostly present in garbage-collected languages at runtime\begin{itemize}
			      \item C\#
			      \item Java
			      \item Scripting languages such as Javscript or Python
		      \end{itemize}
	\end{itemize}

@@

\begin{frame}[fragile]
	\frametitle{Motivating example}
	\begin{lstlisting}
struct person {
	std::string name;
	int yearOfBirth;
	int height;
};
void print(
  std::ostream&s,
  person const& p) {
  s << p.name << '\n'
    << p.yearOfBirth << '\n'
    << p.height << '\n';
}
	\end{lstlisting}

@@
